My wonderful paper

### 2024-11-05 _manuscript/_tex/index.tex
notes on the literature review

This expectation-setting process is often implicit and rarely documented
or discussed in publications. (There are most publication requires open
source code for publication, however, it is no instruction or guidance
on checking \ldots). Yet, making them explicit is crucial for 1) helping
junior researchers interpret results and diagnose the unexpected, 2)
providing checkpoints that support independent replication or
application of methods to new data, 3) aligning assumptino across
researchers from different backgrounds.

@@

@@

@@

\subsection{Data quality checks}\label{data-quality-checks}

\begin{itemize}
\tightlist
\item
  \texttt{pointblank}, \texttt{assertthat}
\end{itemize}

>>>>

This expectation-setting process is often implicit and rarely documented
or discussed in publications. (There are most publication requires open
source code for publication, however, it is no instruction or guidance
on checking \ldots). Yet, making them explicit is crucial for 1) helping
junior researchers interpret results and diagnose the unexpected, 2)
providing checkpoints that support independent replication or
application of methods to new data, 3) aligning assumption across
researchers from different backgrounds.

@@

\citep{peng_diagnosing_2021}

@@

\subsection{Data analysis checks in statistical
software}\label{data-analysis-checks-in-statistical-software}

\begin{itemize}
\tightlist
\item
  The \texttt{assertr} package \citep{assertr} provides a set of
  functions to check the quality of data, including the presence of
  missing values, the distribution of variables, and the relationship
  between variables.
\item
  Similarly, the \texttt{pointblank} package \citep{pointblank} is a
  data validation tool that allows users to define data quality checks.
\end{itemize}

For model checks,

\begin{itemize}
\tightlist
\item
  the \texttt{performance} package \citep{performance} provides a set of
  functions to assess the performance of a model, including residual
  analysis, goodness-of-fit tests.
\item
  The \texttt{yardstick} package \citep{yardstick} provides the
  calculation of model performance metrics in the \texttt{tidymodels}
  \citep{tidymodels} ecosystem.
\end{itemize}

@@

Why develop unit tests in software engineering? Because it is difficult
to predict the outcome of a program, especially when the program is
complex.

Software testing relies on ``oracles'' to provide the expected output
necessary for verifying test results. For example, to test whether the
program correctly calculates 1 + 1, one need to supply the correct
answer, 2. However, establishing this ``correct'' output can sometimes
be challenging, where obtaining a solution may be difficult without the
program itself. This situation leads to the oracle problem
\citep{barr2014oracle}. In data analysis, the similar oracle problem can
happen, as the ``truth'' of an outcome, the expectation, depends on the
underlying theory or interpretation. For example, in a linear regression
model, the significance of a coefficient may be expected or unexpected
based on the theory, making it challenging for researcher with a
different theory to assess the results and the analysis.

Existing tools for checks in data analysis including those check for
data quality and model diagnostics. In software development,

\begin{itemize}
\tightlist
\item
  the \texttt{testthat} package \citep{testthat} provides the
  infrastructure for testing R code. It allows users to write unit tests
  for functions and packages.
\item
  The \texttt{assertthat} package \citep{assertthat} helps to write
  assertion statements that are supposed to be true at a certain point
  in the code for defensive programming.
\end{itemize}

### 2024-11-05 index.qmd
notes on the literature review

This expectation-setting process is often implicit and rarely documented or discussed in publications. (There are most publication requires open source code for publication, however, it is no instruction or guidance on checking ...).  Yet, making them explicit is crucial for 1) helping junior researchers interpret results and diagnose the unexpected, 2) providing checkpoints that support independent replication or application of methods to new data, 3) aligning assumptino across researchers from different backgrounds.

@@

@@

@@

## Data quality checks

- `pointblank`, `assertthat`

>>>>

This expectation-setting process is often implicit and rarely documented or discussed in publications. (There are most publication requires open source code for publication, however, it is no instruction or guidance on checking ...).  Yet, making them explicit is crucial for 1) helping junior researchers interpret results and diagnose the unexpected, 2) providing checkpoints that support independent replication or application of methods to new data, 3) aligning assumption across researchers from different backgrounds.

@@

[@peng_diagnosing_2021]

@@

## Data analysis checks in statistical software

  * The `assertr` package [@assertr] provides a set of functions to check the quality of data, including the presence of missing values, the distribution of variables, and the relationship between variables. 
  * Similarly, the `pointblank` package [@pointblank] is a data validation tool that allows users to define data quality checks.

  For model checks,

  * the `performance` package [@performance] provides a set of functions to assess the performance of a model, including residual analysis, goodness-of-fit tests. 
  * The `yardstick` package [@yardstick] provides the calculation of model performance metrics in the `tidymodels` [@tidymodels] ecosystem.

@@

Why develop unit tests in software engineering? Because it is difficult to predict the outcome of a program, especially when the program is complex. Because the loss associated with a program failure is costly.

Software testing relies on "oracles" to provide the expected output necessary for verifying test results. For example, to test whether the program correctly calculates 1 + 1, one need to supply the correct answer, 2. However, establishing this "correct" output can sometimes be challenging, where obtaining a solution may be difficult without the program itself. This situation leads to the oracle problem [@barr2014oracle]. In data analysis, the similar oracle problem can happen, as the "truth" of an outcome, the expectation, depends on the underlying theory or interpretation. For example, in a linear regression model, the significance of a coefficient may be expected or unexpected based on the theory, making it challenging for researcher with a different theory to assess the results and the analysis.

Existing tools for checks in data analysis including those check for data quality and model diagnostics. In software development,

* the `testthat` package [@testthat] provides the infrastructure for testing R code. It allows users to write unit tests for functions and packages.
* The `assertthat` package [@assertthat] helps to write assertion statements that are supposed to be true at a certain point in the code for defensive programming.
